\chapter{Conclusion}

In this project, multiple components of a liquid-liquid droplet flow reactor for the synthesis of semi-conducting polymers were developed and improved to allow for the application of optimisation software to the system, with the aim of building a self-optimising reactor.  Each area of work will be summarised in turn.

The issue of further polymerisation after the reaction and during the analysis stage of the setup leading to reactor fouling was addressed. Upon addition of a high concentration of a non-selective nickel catalyst Ni(TPP)2(Br2) to the batch synthesis of P3HT, it was shown that polymer growth was successfully terminated. This additional step in the synthetic method was then adapted for the flow reactor, and termed the “termination step”. The modified setup was shown to run for an extended period without fouling or increase in pressure of the analysis step.

Upon inspection of the current separator setup, it was seen that the current method of in-line liquid-liquid separation was unsatisfactory for an automated system due to the infrequent instances of impure separation of reaction solution and carrier liquid. The problem was first addressed through the redesign of the separator equipment for a more facile fabrication and fewer ferrule connections to reduce the risk of leaks. A method of continuous separation analysis was then integrated into the system to provide the system with an indicator of failure of the separator equipment. The newly-designed separator was successfully inserted into the flow reactor and the system was used to monitor the separation of the reaction mixture during the synthesis of P3HT and separate out the product-containing droplets.

In the final stage of the project, the prototype GPC system used to analyse the product of the flow reactor was calibrated to provide a quantitive measurement of the molecular weight of the product polymer. This was achieved through the direct standard calibration method outlined by C. Wu. A calibration set of P3HT of a range of molecular weights were synthesised and used to calibrate the prototype GPC against a commercial system. The calibrated prototype was then tested in a flow synthesis.

